R Notebook

### 2023-03-21 Analysis tests.Rmd
Changed the README to come from and RMD file

```{r}
df <- read_csv("data/funda_buy_21-03-2023(sample100p).csv")

@@

```{r}
df_test <- df %>% 
  top_n(10) %>% 
  separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4"), " ") %>% 
  mutate(addressline_city = paste(city, optional1, optional2, optional3, optional4),
         addressline_zip = paste(zip, letters),
         addresszip = paste0(address, ", ",addressline_zip, ", ", city, ", Nederland")) %>% 
  select(-optional1, -optional2, -optional3, -optional4) %>% 
  geocode(addresszip, method = 'osm', lat = latitude , long = longitude)

>>>>

```{r}
df <- read_csv("data/test/funda_buy_21-03-2023(sample100p).csv")

@@

```{r}
df_new <- df %>% 
  separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4"), " ") %>% 
  mutate(addressline_city = paste(city, optional1, optional2, optional3, optional4),
         addressline_zip = paste(zip, letters),
         addresszip = paste0(address, ", ",addressline_zip, ", ", city, ", Nederland")) %>% 
  select(-optional1, -optional2, -optional3, -optional4) %>% 
  geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
write.csv(df_new,"data/funda_buy_21-03-2023(sample100p)latlon.csv")
